---
title: ""
output: html_notebook
---

# The data  
All tracks are stored in a single data.table object. Each line represents one track.

```{r}
head(tracks)
```

# Statistical distribution of swimming speed 
The distribution of mean track speed is not normal, which would be a problem for statistics such as t-tests. It seems, however, that mean of log speed takes it much closer to normality. The blue dashed line in the plot below shows fit of normal distribution to the data.
```{r}
speed_mean_NON <- tracks[n>60 & Condition == "NON", sapply(Speed, mean)]
speed_mean_NON_log <- tracks[n>60 & Condition == "NON", sapply(Speed, function(x) mean(log(x)))]

tdn <- testDistribution(speed_mean_NON, "normal")
plot(tdn)
tdn <- testDistribution(speed_mean_NON_log, "normal")
plot(tdn)
```

# Speed vs shape
Let's see if there is a correlation between the speed and shape - if it is strong, we could just use speed to compare the lines
```{r}
tracks[ n > 60,
           .(Shape = mean(sapply(DP_simplify, sum)),
             Log_speed = mean(sapply(Speed, function(x) (mean(log(x))))),
             Shape_SE = sd(sapply(DP_simplify, sum))/sqrt(length(DP_simplify)),
             Log_speed_SE = sd(sapply(Speed, function(x) (mean(log(x)))))/sqrt(length(DP_simplify))
           ),
           by = .(Line, Condition)
           ][,ggplot(.SD, aes(Log_speed, Shape, colour = Condition, fill = Condition))+
               geom_point(shape = 21, colour = 'black', size = 2)+
               geom_text(aes(label=Line),hjust= -0.1, vjust= -0.1, size = 3.5)+
               labs(title = "Mean shape and log speed for each cell line")
             ]

```

One can also plot mean for each individual FOV

```{r}
tracks[ n > 60,
           .(Shape = mean(sapply(DP_simplify, sum)),
             Log_speed = mean(sapply(Speed, function(x) (mean(log(x))))),
             Shape_SE = sd(sapply(DP_simplify, sum))/sqrt(length(DP_simplify)),
             Log_speed_SE = sd(sapply(Speed, function(x) (mean(log(x)))))/sqrt(length(DP_simplify))
           ),
           by = .(Line, Condition, movie = paste(Experiment, Field))
           ][,ggplot(.SD, aes(Log_speed, Shape, group = movie, colour = Condition))+
               geom_point()+
               #geom_errorbar(aes(ymin=Shape-Shape_SE, ymax=Shape+Shape_SE), width=.005) +
               #geom_errorbarh(aes(xmin=Log_speed - Log_speed_SE, xmax = Log_speed + Log_speed_SE), height=.05) +
               #geom_text(aes(label=paste(Line, Condition)),hjust= -0.1, vjust= -0.1, size = 0)+
               facet_wrap(~Line)+
               labs(title = "Mean shape and log_speed for individual movies")
             ]
```

# Do the cells speed up during acquisition?
It looks like they speed up during first three movies. Perhaps the slide is warming up.

```{r}
tracks[ n > 60 & Condition == 'NON',
        .(
          Shape = (sapply(DP_simplify, sum)),
          Speed = (sapply(Speed, function(x) (mean((x)))))
        ),
        by = .(Line, Condition, movie = Field)
        ][,
          ggplot(.SD)+
            geom_boxplot(aes(factor(movie, levels = 1:20), Speed))+
            labs(title = "Mean speed by imaging position")+
            theme(legend.position = 'none')
          ]
```

One can zoom in using command coord_cartesian(ylim=c(3, 8)) 

```{r}
tracks[ n > 60 & Condition == 'NON',
        .(
          Shape = (sapply(DP_simplify, sum)),
          Speed = (sapply(Speed, function(x) (mean((x)))))
        ),
        by = .(Line, Condition, movie = Field)
        ][,
          ggplot(.SD)+
            geom_boxplot(aes(factor(movie, levels = 1:20), Speed))+
            labs(title = "Mean speed for individual imaging positions")+
            theme(legend.position = 'none')+
            coord_cartesian(ylim=c(3, 8))
          ]
```
